Concurrent Programming in Harmony

### 2022-01-06 book/paper.tex
Added an exercise

>>>>

\section*{Exercises}
\begin{problems}
\item (This is just for fun or exercise as it is not a concurrent or
distributed problem.)
Implement a Harmony program that finds solutions to the
``cabbage, goat, and wolf'' problem.  In this problem, a person
accompanied by these three items has to cross a stream in a small
boat, but can only take one item at a time. So, the person has to
cross back and forth several times, leaving two items on one or
the other shore by themselves.
Unfortunately, if left to themselves, the goat would
eat the cabbage and the wolf would eat the goat.  What crossings
does the person need to make in order not to lose any items?
\end{problems}
